---
title: "NP NCR Hamming Distances"
author: "Alexandra Christopoulos"
date: "2023-03-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "C:/Users/Lexie Christopoulos/Repos/GenomeSequencing-/db/",echo = TRUE)
```

#in console: setwd("C:/Users/Lexie Christopoulos/Repos/GenomeSequencing-/db/NP")

NP_H1 Forward 1.5 primer NCR Hamming Distances 
```{r}
NP_H1_F <-read.csv("hamming_distance_results/NP_H1_NP_Forward_1.5_results_NCR.csv")

NP_H1_1 <- NP_H1_F[-c(2902),]

barplot(table(NP_H1_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,3000))
```

NP_H1 Reverse 2.3 primer NCR Hamming Distances 
```{r}
NP_H1_R <-read.csv("hamming_distance_results/NP_H1_NP_Reverse_2.3_results_NCR.csv")

NP_H1_2 <- NP_H1_R[-c(2902),]

barplot(table(NP_H1_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,2500))

```

NP_H3 Forward 1.5 primer NCR Hamming Distances 
```{r}
NP_H3_F <-read.csv("hamming_distance_results/NP_H3_NP_Forward_1.5_results_NCR.csv")

NP_H3_1 <- NP_H3_F[-c(5046),]

barplot(table(NP_H3_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,6000))
```

NP_H3 Reverse 2.3 primer NCR Hamming Distance Results 
```{r}
NP_H3_R <-read.csv("hamming_distance_results/NP_H3_NP_Reverse_2.3_results_NCR.csv")

NP_H3_2 <- NP_H3_R[-c(5046),]

barplot(table(NP_H3_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,5500))

```

NP_H5 Forward 1.5 primer Hamming Distances 
```{r}
NP_H5_F <-read.csv("hamming_distance_results/NP_H5_NP_Forward_1.5_results_NCR.csv")

NP_H5_1 <- NP_H5_F[-c(17),]

barplot(table(NP_H5_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,20))
```

NP_H5 Reverse 2.3 primer NCR Hamming Distance Results
```{r}
NP_H5_R <-read.csv("hamming_distance_results/NP_H5_NP_Reverse_2.3_results_NCR.csv")

NP_H5_2 <- NP_H5_R[-c(17),]

barplot(table(NP_H5_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,20))
```

NP_H7 Forward 1.5 primer NCR Hamming Distances 
```{r}
NP_H7_F <-read.csv("hamming_distance_results/NP_H7_NP_Forward_1.5_results_NCR.csv")

NP_H7_1 <- NP_H7_F[-c(31),]

barplot(table(NP_H7_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,35))
```

NP_H7 Reverse 2.3 primer NCR Hamming Distances 
```{r}
NP_H7_R <-read.csv("hamming_distance_results/NP_H7_NP_Reverse_2.3_results_NCR.csv")

NP_H7_2 <- NP_H7_R[-c(31),]

barplot(table(NP_H7_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,35))
```

NP_H9 Forward 1.5 primer NCR Hamming Distances 
```{r}
NP_H9_F <-read.csv("hamming_distance_results/NP_H9_NP_Forward_1.5_results_NCR.csv")

NP_H9_1 <- NP_H9_F[-c(19),]

barplot(table(NP_H9_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,20))
```

NP_H9 Reverse 2.3 primer NCR Hamming Distances 
```{r}
NP_H9_R <-read.csv("hamming_distance_results/NP_H9_NP_Reverse_2.3_results_NCR.csv")

NP_H9_2 <- NP_H9_R[-c(19),]

barplot(table(NP_H9_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,20))
```