---
title: "NA NCR Hamming Distances"
author: "Alexandra Christopoulos"
date: "2023-03-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "C:/Users/Lexie Christopoulos/Repos/GenomeSequencing-/db/", echo = TRUE)
```

#in console: setwd("C:/Users/Lexie Christopoulos/Repos/GenomeSequencing-/db/NA")

NA_H1 Forward 1.2 primer NCR Hamming Distances 
```{r}
NA_H1_F <-read.csv("hamming_distance_results/NA_H1_NA_Forward_1.2_results_NCR.csv")

NA_H1_1 <- NA_H1_F[-c(67),]

barplot(table(NA_H1_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,80))
```

NA_H1 Reverse 2.1 primer NCR Hamming Distances 
```{r}
NA_H1_R <-read.csv("hamming_distance_results/NA_H1_NA_Reverse_2.1_results_NCR.csv")

NA_H1_2 <- NA_H1_R[-c(67),]

barplot(table(NA_H1_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,80))
```

NA_H3 Forward 1.2 primer NCR Hamming Distances 
```{r}
NA_H3_F <-read.csv("hamming_distance_results/NA_H3_NA_Forward_1.2_results_NCR.csv")

NA_H3_1 <- NA_H3_F[-c(4900),]

barplot(table(NA_H3_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,5000))
```

NA_H3 Reverse 2.1 primer NCR Hamming Distances 
```{r}
NA_H3_R <-read.csv("hamming_distance_results/NA_H3_NA_Reverse_2.1_results_NCR.csv")

NA_H3_2 <- NA_H3_R[-c(4900),]

barplot(table(NA_H3_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,5000))

```

NA_H5 Forward 1.2 primer NCR Hamming Distances 
```{r}
NA_H5_F <-read.csv("hamming_distance_results/NA_H5_NA_Forward_1.2_results_NCR.csv")

NA_H5_1 <- NA_H5_F[-c(19),]

barplot(table(NA_H5_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,15))

```

NA_H5 Reverse 2.1 primer NCR Hamming Distances 
```{r}
NA_H5_R <-read.csv("hamming_distance_results/NA_H5_NA_Reverse_2.1_results.csv")

NA_H5_2 <- NA_H5_R[-c(19),]

barplot(table(NA_H5_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,15))
```

NA_H7 Forward 1.2 primer NCR Hamming Distances 
```{r}
NA_H7_F <-read.csv("hamming_distance_results/NA_H7_NA_Forward_1.2_results_NCR.csv")

NA_H7_1 <- NA_H7_F[-c(71),]

barplot(table(NA_H7_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,75))
```

NA_H7 Reverse 2.1 primer NCR Hamming Distances 
```{r}
NA_H7_R <-read.csv("hamming_distance_results/NA_H7_NA_Reverse_2.1_results_NCR.csv")

NA_H7_2 <- NA_H7_R[-c(71),]

barplot(table(NA_H7_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,75))
```

NA_H9 Forward 1.2 primer NCR Hamming Distances 
```{r}
NA_H9_F <-read.csv("hamming_distance_results/NA_H9_NA_Forward_1.2_results_NCR.csv")

NA_H9_1 <- NA_H9_F[-c(17),]

barplot(table(NA_H9_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,20))
```

NA_H9 Reverse 2.1 primer NCR Hamming Distances 
```{r}
NA_H9_R <-read.csv("hamming_distance_results/NA_H9_NA_Reverse_2.1_results_NCR.csv")

NA_H9_2 <- NA_H9_R[-c(17),]

barplot(table(NA_H9_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,15))
```

