---
title: "PB1 Hamming Distances"
author: "Alexandra Christopoulos"
date: "2023-03-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "C:/Users/Lexie Christopoulos/Repos/GenomeSequencing-/db/", echo = TRUE)
```

#in console: setwd("C:/Users/Lexie Christopoulos/Repos/GenomeSequencing-/db/PB1")

PB1_H1 Forward 1.2 primer Hamming Distances 
```{r}
PB1_H1_F <-read.csv("hamming_distance_results/PB1_H1_PB1_Forward_1.2_results.csv")

PB1_H1_1 <- PB1_H1_F[-c(3296),]

barplot(table(PB1_H1_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,3000))
```

PB1_H1 Reverse 2.3 primer Hamming Distances 
```{r}
PB1_H1_R <-read.csv("hamming_distance_results/PB1_H1_PB1_Reverse_2.3_results.csv")

PB1_H1_2 <- PB1_H1_R[-c(3296),]

barplot(table(PB1_H1_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,3000))
```

PB1_H3 Forward 1.2 primer Hamming Distances 
```{r}
PB1_H3_F <-read.csv("hamming_distance_results/PB1_H3_PB1_Forward_1.2_results.csv")

PB1_H3_1 <- PB1_H3_F[-c(7357),]

barplot(table(PB1_H3_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,5500))
```

PB1_H3 Reverse 2.3 primer Hamming Distances 
```{r}
PB1_H3_R <-read.csv("hamming_distance_results/PB1_H3_PB1_Reverse_2.3_results.csv")

PB1_H3_2 <- PB1_H3_R[-c(7357),]

barplot(table(PB1_H3_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,5500))
```

PB1_H5 Froward 1.2 primer Hamming Distances 
```{r}
PB1_H5_F <-read.csv("hamming_distance_results/PB1_H5_PB1_Forward_1.2_results.csv")

PB1_H5_1 <- PB1_H5_F[-c(4),]

barplot(table(PB1_H5_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,5))
```

PB1_H5 Reverse 2.3 primer Hamming Distances 
```{r}
PB1_H5_R <-read.csv("hamming_distance_results/PB1_H5_PB1_Reverse_2.3_results.csv")

PB1_H5_2 <- PB1_H5_R[-c(4),]

barplot(table(PB1_H5_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,5))
```

PB1_H7 Forward 1.2 primer Hamming Distances 
```{r}
PB1_H7_F <-read.csv("hamming_distance_results/PB1_H7_PB1_Forward_1.2_results.csv")

PB1_H7_1 <- PB1_H7_F[-c(17),]

barplot(table(PB1_H7_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,15))
```

PB1_H7 Reverse 2.3 primer Hamming Distances
```{r}
PB1_H7_R <-read.csv("hamming_distance_results/PB1_H7_PB1_Reverse_2.3_results.csv")

PB1_H7_2 <- PB1_H7_R[-c(17),]

barplot(table(PB1_H7_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,15))

```

PB1_H9 Forward 1.2 primer Hamming Distance 
```{r}
PB1_H9_F <-read.csv("hamming_distance_results/PB1_H9_PB1_Forward_1.2_results.csv")

PB1_H9_1 <- PB1_H9_F[-c(3),]

barplot(table(PB1_H9_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,5))
```

PB1_H9 Reverse 2.3 primer Hamming Distances 
```{r}
PB1_H9_R <-read.csv("hamming_distance_results/PB1_H9_PB1_Reverse_2.3_results.csv")

PB1_H9_2 <- PB1_H9_R[-c(3),]

barplot(table(PB1_H9_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,5))
```

