---
title: "HA NCR Hamming Distances"
author: "Alexandra Christopoulos"
date: "2023-03-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "C:/Users/Lexie Christopoulos/Repos/GenomeSequencing-/db/", echo = TRUE)
```


#in console: setwd("C:/Users/Lexie Christopoulos/Repos/GenomeSequencing-/db/HA")

HA_H1 Forward 1.6 primer NCR hamming distances 
```{r}
HA_H1_F1 <-read.csv("hamming_distance_results/HA_H1_HA_Forward_1.6_results_NCR.csv")

HA_H1_1 <- HA_H1_F1[-c(4023, 4024, 4025),]

barplot(table(HA_H1_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,3500))
```

HA_H1 Forward 1.7 primer NCR Hamming Distances 
```{r}
HA_H1_F2 <-read.csv("hamming_distance_results/HA_H1_HA_Forward_1.7_results_NCR.csv")

HA_H1_2 <- HA_H1_F2[-c(4023, 4024, 4025),]

barplot(table(HA_H1_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences",ylim = c(0,3500))
```

HA_H1 Reverse 2.3 primer NCR Hamming Distances 
```{r}
HA_H1_R <-read.csv("hamming_distance_results/HA_H1_HA_Reverse_2.3_results_NCR.csv")

HA_H1_3 <- HA_H1_R[-c(4023,4024),]

barplot(table(HA_H1_3$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,4000))
```

HA_H3 Forward 1.6 primer NCR Hamming Distances 
```{r}
HA_H3_F1 <-read.csv("hamming_distance_results/HA_H3_HA_Forward_1.6_results_NCR.csv")

HA_H3_1 <- HA_H3_F1[-c(5490, 5491, 5492),]

barplot(table(HA_H3_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,5000))

```

HA_H3 Forward 1.7 primer NCR Hamming Distances 
```{r}
HA_H3_F2 <-read.csv("hamming_distance_results/HA_H3_HA_Forward_1.7_results_NCR.csv")

HA_H3_2 <- HA_H3_F2[-c(5490, 5491, 5492),]

barplot(table(HA_H3_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences",ylim = c(0,5000))
```

HA_H3 Reverse 2.3 primer NCR Hamming Distances 
```{r}
HA_H3_R <-read.csv("hamming_distance_results/HA_H3_HA_Reverse_2.3_results_NCR.csv")

HA_H3_3 <- HA_H3_R[-c(5490, 5491),]

barplot(table(HA_H3_3$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,6000))
```

HA_H5 Forward 1.6 primer NCR Hamming Distances 
```{r}
HA_H5_F1 <-read.csv("hamming_distance_results/HA_H5_HA_Forward_1.6_results_NCR.csv")

HA_H5_1 <- HA_H5_F1[-c(19, 20, 21),]

barplot(table(HA_H5_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences",ylim = c(0,15))
```

HA_H5 Forward 1.7 primer NCR Hamming Distances 
```{r}
HA_H5_F2 <-read.csv("hamming_distance_results/HA_H5_HA_Forward_1.7_results_NCR.csv")

HA_H5_2 <- HA_H5_F2[-c(19, 20, 21),]

barplot(table(HA_H5_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences",ylim = c(0,10))
```

HA_H5 Reverse 2.3 primer NCR Hamming Distances 
```{r}
HA_H5_R <-read.csv("hamming_distance_results/HA_H5_HA_Reverse_2.3_results_NCR.csv")

HA_H5_3 <- HA_H5_R[-c(19, 20),]

barplot(table(HA_H5_3$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,15))
```

HA_H7 Forward 1.6 primer NCR Hamming Distances 
```{r}
HA_H7_F1 <-read.csv("hamming_distance_results/HA_H7_HA_Forward_1.6_results_NCR.csv")

HA_H7_1 <- HA_H7_F1[-c(68, 69, 70),]

barplot(table(HA_H7_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences",ylim = c(0,70))
```

HA_H7 Forward 1.7 primer NCR Hamming Distances 
```{r}
HA_H7_F2 <-read.csv("hamming_distance_results/HA_H7_HA_Forward_1.7_results_NCR.csv")

HA_H7_2 <- HA_H7_F2[-c(68, 69, 70),]

barplot(table(HA_H7_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences",ylim = c(0,50))
```

HA_H7 Reverse 2.3 primer NCR Hamming Distances 
```{r}
HA_H7_R <-read.csv("hamming_distance_results/HA_H7_HA_Reverse_2.3_results_NCR.csv")

HA_H7_3 <- HA_H7_R[-c(68, 69),]

barplot(table(HA_H7_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences",ylim = c(0,50))
```

HA_H9 Forward 1.6 primer NCR Hamming Distances 
```{r}
HA_H9_F1 <-read.csv("hamming_distance_results/HA_H9_HA_Forward_1.6_results_NCR.csv")

HA_H9_1 <- HA_H9_F1[-c(21,22,23),]

barplot(table(HA_H9_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences",ylim = c(0,15))

```

HA_H9 Forward 1.7 primer NCR Hamming Distances 
```{r}
HA_H9_F2 <-read.csv("hamming_distance_results/HA_H9_HA_Forward_1.7_results_NCR.csv")

HA_H9_2 <- HA_H9_F2[-c(21,22,23),]

barplot(table(HA_H9_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences",ylim = c(0,20))
```

HA_H9 Reverse 2.3 primer NCR Hamming Distances 
```{r}
HA_H9_R <-read.csv("hamming_distance_results/HA_H9_HA_Reverse_2.3_results_NCR.csv")

HA_H9_3 <- HA_H9_R[-c(21,22),]

barplot(table(HA_H9_3$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences",ylim = c(0,15))
```

