---
title: "PB2 NCR Hamming Distances"
author: "Alexandra Christopoulos"
date: "2023-03-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "C:/Users/Lexie Christopoulos/Repos/GenomeSequencing-/db/", echo = TRUE)
```

#in console: setwd("C:/Users/Lexie Christopoulos/Repos/GenomeSequencing-/db/PB2")

PB2_H1 Forward 1.1 primer NCR Hamming Distances
```{r}
PB2_H1_F <-read.csv("hamming_distance_results/PB2_H1_PB2_Forward_1.1_results_NCR.csv")

PB2_H1_1 <- PB2_H1_F[-c(2570),]

barplot(table(PB2_H1_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,2500))
```


PB2_H1 Reverse 2.3 primer NCR Hamming Distances 
```{r}
PB2_H1_R <-read.csv("hamming_distance_results/PB2_H1_PB2_Reverse_2.3_results_NCR.csv")

PB2_H1_2 <- PB2_H1_R[-c(2570),]

barplot(table(PB2_H1_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,2500))
```

PB2_H3 Forward 1.1 primer NCR Hamming Distances 
```{r}
PB2_H3_F <-read.csv("hamming_distance_results/PB2_H3_PB2_Forward_1.1_results_NCR.csv")

PB2_H3_1 <- PB2_H3_F[-c(4627),]

barplot(table(PB2_H3_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,4500))
```

PB1_H3 Reverse 2.3 primer NCR Hamming Distances 
```{r}
PB2_H3_R <-read.csv("hamming_distance_results/PB2_H3_PB2_Reverse_2.3_results_NCR.csv")

PB2_H3_2 <- PB2_H3_R[-c(4627),]

barplot(table(PB2_H3_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,5000))
```

PB2_H5 Forward 1.1 primer NCR Hamming Distances 
```{r}
PB2_H5_F <-read.csv("hamming_distance_results/PB2_H5_PB2_Forward_1.1_results_NCR.csv")

PB2_H5_1 <- PB2_H5_F[-c(8),]

barplot(table(PB2_H5_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,5))
```

PB2_H5 Reverse 2.3 primer NCR Hamming Distances 
```{r}
PB2_H5_R <-read.csv("hamming_distance_results/PB2_H5_PB2_Reverse_2.3_results_NCR.csv")

PB2_H5_2 <- PB2_H5_R[-c(8),]

barplot(table(PB2_H5_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,5))
```

PB2_H7 Forward 1.1 primer NCR Hamming Distances 
```{r}
PB2_H7_F <-read.csv("hamming_distance_results/PB2_H7_PB2_Forward_1.1_results_NCR.csv")

PB2_H7_1 <- PB2_H7_F[-c(46),]

barplot(table(PB2_H7_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,25))
```

PB2_H7 Reverse 2.3 primer NCR Hamming Distances 
```{r}
PB2_H7_R <-read.csv("hamming_distance_results/PB2_H7_PB2_Reverse_2.3_results_NCR.csv")

PB2_H7_2 <- PB2_H7_R[-c(46),]

barplot(table(PB2_H7_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,50))
```

PB1_H9 Forward 1.1 primer NCR Hamming Distances 
```{r}
PB2_H9_F <-read.csv("hamming_distance_results/PB2_H9_PB2_Forward_1.1_results_NCR.csv")

PB2_H9_1 <- PB2_H9_F[-c(9),]

barplot(table(PB2_H9_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,6))
```

PB2_H9 Reverse 2.3 primer NCR Hamming Distances 
```{r}
PB2_H9_R <-read.csv("hamming_distance_results/PB2_H9_PB2_Reverse_2.3_results_NCR.csv")

PB2_H9_2 <- PB2_H9_R[-c(9),]

barplot(table(PB2_H9_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,10))
```
