---
title: "NS Hamming Distances"
author: "Alexandra Christopoulos"
date: "2023-03-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "C:/Users/Lexie Christopoulos/Repos/GenomeSequencing-/db/", echo = TRUE)
```

#in console: setwd("C:/Users/Lexie Christopoulos/Repos/GenomeSequencing-/db/NS")

NS_H1 Forward 1.2 primer Hamming Distances 
```{r}
NS_H1_F <-read.csv("hamming_distance_results/NS_H1_NS_Forward_1.2_results.csv")

NS_H1_1 <- NS_H1_F[-c(2165,2166),]

barplot(table(NS_H1_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,2000))
```

NS_H1 Reverse 2.1 primer Hamming Distances 
```{r}
NS_H1_R <-read.csv("hamming_distance_results/NS_H1_NS_Reverse_2.1_results.csv")

NS_H1_2 <- NS_H1_R[-c(2165,2166),]

barplot(table(NS_H1_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,2000))

```

NS_H3 Forward 1.2 primer Hamming Distances 
```{r}
NS_H3_F <-read.csv("hamming_distance_results/NS_H3_NS_Forward_1.2_results.csv")

NS_H3_1 <- NS_H3_F[-c(4076,4077),]

barplot(table(NS_H3_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,3500))
```

NS_H3 Reverse 1.2 primer Hamming Distances 
```{r}
NS_H3_R <-read.csv("hamming_distance_results/NS_H3_NS_Reverse_2.1_results.csv")

NS_H3_2 <- NS_H3_R[-c(4076,4077),]

barplot(table(NS_H3_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,4500))
```

NS_H5 Forward 1.2 primer Hamming Distances 
```{r}
NS_H5_F <-read.csv("hamming_distance_results/NS_H5_NS_Forward_1.2_results.csv")

NS_H5_1 <- NS_H5_F[-c(7,8),]

barplot(table(NS_H5_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,10))
```

NS_H5 Reverse 2.1 primer Hamming Distances 
```{r}
NS_H5_R <-read.csv("hamming_distance_results/NS_H5_NS_Reverse_2.1_results.csv")

NS_H5_2 <- NS_H5_R[-c(7,8),]

barplot(table(NS_H5_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,10))
```

NS_H7 Forward 1.2 primer Hamming Distances 
```{r}
NS_H7_F <-read.csv("hamming_distance_results/NS_H7_NS_Forward_1.2_results.csv")

NS_H7_1 <- NS_H7_F[-c(19,20),]

barplot(table(NS_H7_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,20))
```

NS_H7 Reverse 2.1 primer Hamming Distances 
```{r}
NS_H7_R <-read.csv("hamming_distance_results/NS_H7_NS_Reverse_2.1_results.csv")

NS_H7_2 <- NS_H7_R[-c(19,20),]

barplot(table(NS_H7_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,20))

```

NS_H9 Forward 1.2 primer Hamming Distances 
```{r}
NS_H9_F <-read.csv("hamming_distance_results/NS_H9_NS_Forward_1.2_results.csv")

NS_H9_1 <- NS_H9_F[-c(4,5),]

barplot(table(NS_H9_1$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,5))
```

NS_H9 Reverse 2.1 primer Hamming Distances 
```{r}
NS_H9_R <-read.csv("hamming_distance_results/NS_H9_NS_Reverse_2.1_results.csv")

NS_H9_2 <- NS_H9_R[-c(4,5),]

barplot(table(NS_H9_2$hamming_distance), xlab = "Hamming Distance", ylab = "Number of Sequences", ylim = c(0,5))
```

